Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-02 paper_jasa.tex
reasoning plot added

\green{I find this plot really confusing! Can we just look at whether they selected choice ``clustering visible'' or not, if they were correct?}

\begin{figure}[hbtp]
   \centering
       \scalebox{0.60}{\includegraphics{choice_reason.pdf}}
       \caption{Reasons for choosing the plot in a lineup for experiment 3. Reason 12 means both reasons 1 and 2 are chosen. Number of subjects choosing that reason are shown on the right hand side. Notice that 345 people choose only reason (3) "Clustering visible", out of whom 64\% got the actual plot (proportion correct = 0.64), which indicates there are number of people who choose the right plot for wrong reason (Type-III error). Those who chose reason 123 got the actual plot about 97\% times.}
       \label{fig:choice_reason}
\end{figure}

>>>>

\green{I find this plot really confusing! Can we just look at whether they selected choice ``clustering visible'' or not, if they were correct?} \blue{Is the right hand side plot in figure \ref{fig:choice_reason} ok? Should we remove the left plot?}

\begin{figure}[hbtp]
   \centering
       \scalebox{0.60}{\includegraphics{choice_reason.pdf}}
       \scalebox{0.60}{\includegraphics{choice_reason_count.pdf}}
       \caption{Reasons for choosing the plot in a lineup for experiment 3. Reason 12 means both reasons 1 and 2 are chosen. Number of subjects choosing that reason are shown on the right hand side. Notice that 345 people choose only reason (3) "Clustering visible", out of whom 64\% got the actual plot (proportion correct = 0.64), which indicates there are number of people who choose the right plot for wrong reason (Type-III error). Those who chose reason 123 got the actual plot about 97\% times.}
       \label{fig:choice_reason}
\end{figure}
